---
title: "Analysis for OSC Data - Birth Experience"
author: "Aarthi Ravi"
date: "25/08/2021"
output:
  pdf_document: default
  html_document: default
---
```{r setup, warning=FALSE,message=FALSE}

require("knitr")
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(tidy.opts=list(width.cutoff=50),tidy=TRUE)

library(data.table)
library(tidyverse)
library(magrittr)
library(car)
library(gridExtra)
library(psych)
library(ggplot2)
library(multcomp)
library(plotly)
library(apaTables)
library(dplyr)
library(rstatix)
library(plyr)
```

# Import Datasets - Full data and Data of correct trials only

```{r data}
data <- read.csv ("OSC_Full_Data.csv")
data_cue <- read.csv ("OSC_cue_trials.csv")
data_nocue <- read.csv ("OSC_nocue_trials.csv")
```

# Descriptives/ Preliminary Analyses

```{r descriptives data}
data1 <- select (data, ID, AGE, BIRTH_EXP, DIS,TRIAL_TYPE, REAC_TIME, ACCURACY, REAC_TIME_CT)
head (data1)
summary (data1)
describe (data1)

data2 <- select (data_cue, ID, AGE, BIRTH_EXP, DIS, REAC_TIME, ACCURACY, REAC_TIME_CT)
head (data2)
summary (data2)
describe (data2)

data3 <- select (data_nocue, ID, AGE, BIRTH_EXP, DIS, REAC_TIME, ACCURACY, REAC_TIME_CT)
head (data3)
summary (data3)
describe (data3)

```
# Table : Number of Participants in each Group

```{r descriptives table, echo =FALSE}
d1 <- filter (data1, AGE < 9 )
d2 <- filter (data1, (AGE<12 & AGE>8))
d3 <- filter (data1, AGE>11)
d4 <- filter (data1, BIRTH_EXP == "V")
d5 <- filter (data1, BIRTH_EXP == "C")
d6 <- filter (data1, DIS == "Y")


number_group <- c(nrow(d1),nrow(d2),nrow(d3),nrow(d4),nrow(d5),nrow(d6))
part_demographics <- data.frame(cbind(nrow(d1),nrow(d2),nrow(d3),nrow(d4),nrow(d5),nrow(d6)))

names (part_demographics) <- c("Age_Group1 (6 to 8 yrs)", "Age_Group2 (9 to 11 yrs)", "Age_Group3 (12< yrs)", "Vaginally_born", "C-sec_born", "Gen_dis")


kable (part_demographics, align = "cccccc")
```

```{r Factors , echo=FALSE, results='hide'}
# Creating factors
data1$AGE_GROUPS <- factor(data1$AGE)
data1$AGE_GROUPS <- data1$AGE
data1$AGE_GROUPS[which(data1$AGE < 9)]<- "1"
data1$AGE_GROUPS[which(data1$AGE<12 & data1$AGE>8)]<- "2"
data1$AGE_GROUPS[which(data1$AGE > 11)]<- "3"

data1$AGE_GROUPS <- as.factor (data1$AGE_GROUPS)
data1$BIRTH_EXP <- as.factor (data1$BIRTH_EXP)
data1$TRIAL_TYPE <- as.factor (data1$TRIAL_TYPE)


# Creating factors cue 
data2$AGE_GROUPS <- factor(data2$AGE)
data2$AGE_GROUPS <- data2$AGE
data2$AGE_GROUPS[which(data2$AGE < 9)]<- "1"
data2$AGE_GROUPS[which(data2$AGE<12 & data2$AGE>8)]<- "2"
data2$AGE_GROUPS[which(data2$AGE > 11)]<- "3"

data2$AGE_GROUPS <- as.factor (data2$AGE_GROUPS)
data2$BIRTH_EXP <- as.factor (data2$BIRTH_EXP)



# Creating factors nocue
data3$AGE_GROUPS <- factor(data3$AGE)
data3$AGE_GROUPS <- data3$AGE
data3$AGE_GROUPS[which(data3$AGE < 9)]<- "1"
data3$AGE_GROUPS[which(data3$AGE<12 & data3$AGE>8)]<- "2"
data3$AGE_GROUPS[which(data3$AGE > 11)]<- "3"

data3$AGE_GROUPS <- as.factor (data3$AGE_GROUPS)
data3$BIRTH_EXP <- as.factor (data3$BIRTH_EXP)
```

# Graphs

### Function to calculate mean and standard deviation of each group

```{r function,  echo=FALSE}

## Gives count, mean, standard deviation, standard error of the mean, and confidence interval (default 95%).
##   data: a data frame.
##   measurevar: the name of a column that contains the variable to be summariezed
##   groupvars: a vector containing names of columns that contain grouping variables
##   na.rm: a boolean that indicates whether to ignore NA's
##   conf.interval: the percent range of the confidence interval (default is 95%)
summarySE <- function(data=NULL, measurevar, groupvars=NULL, na.rm=FALSE,
                      conf.interval=.95, .drop=TRUE) {
    library(plyr)

    # New version of length which can handle NA's: if na.rm==T, don't count them
    length2 <- function (x, na.rm=FALSE) {
        if (na.rm) sum(!is.na(x))
        else       length(x)
    }

    # This does the summary. For each group's data frame, return a vector with
    # N, mean, and sd
    datac <- ddply(data, groupvars, .drop=.drop,
      .fun = function(xx, col) {
        c(N    = length2(xx[[col]], na.rm=na.rm),
          mean = mean   (xx[[col]], na.rm=na.rm),
          sd   = sd     (xx[[col]], na.rm=na.rm)
        )
      },
      measurevar
    )

    # Rename the "mean" column    
    datac <- rename(datac, c("mean" = measurevar))

    datac$se <- datac$sd / sqrt(datac$N)  # Calculate standard error of the mean

    # Confidence interval multiplier for standard error
    # Calculate t-statistic for confidence interval: 
    # e.g., if conf.interval is .95, use .975 (above/below), and use df=N-1
    ciMult <- qt(conf.interval/2 + .5, datac$N-1)
    datac$ci <- datac$se * ciMult

    return(datac)
}

```


## 1. Accuracy

```{r Graph 1}
# Graph 1 for Retrieval Phase 1
fd_graph <- summarySE(data1, measurevar="ACCURACY", groupvars=c("AGE_GROUPS","BIRTH_EXP","TRIAL_TYPE"))
head (fd_graph)

pd <- position_dodge(0.1)
ggplot(fd_graph, aes(x=AGE_GROUPS , y= ACCURACY, group=BIRTH_EXP, color=BIRTH_EXP)) + 
  facet_grid(TRIAL_TYPE~.)+
    geom_errorbar(aes(ymin=ACCURACY-se, ymax=ACCURACY+se), colour="black", width=.1, position=pd, size = 1) +
    geom_line(position=pd, size = 1.1) +
    geom_point(position=pd, size=3, shape=21, fill="white") + # 21 is filled circle
    xlab("AGE GROUPS (years)") +
    ylab("ACCURACY") +
    scale_colour_hue(name = "Birth Experience",
                     breaks=c("C", "V"),
                     labels=c("C-section", "Vaginal"),
                     l=40) + 
    theme(legend.position = "bottom")+ 
    ggtitle("Accuracy in Each Trial Condition for Birth Experience") + # Use darker colors, lightness=40
    expand_limits(y=c(0.2, 0.6)) +                        # Expand y range
    theme_bw()
   
```


## 2. Reaction Time

```{r Graph 2}
# Graph 1 for Retrieval Phase 1
fd_graph_RT <- summarySE(data1, measurevar="REAC_TIME_CT", groupvars=c("AGE_GROUPS","BIRTH_EXP","TRIAL_TYPE"))
head (fd_graph_RT)

pd <- position_dodge(0.1)
ggplot(fd_graph_RT, aes(x=AGE_GROUPS , y= REAC_TIME_CT , group=BIRTH_EXP, color=BIRTH_EXP)) + 
  facet_grid(TRIAL_TYPE~.)+
    geom_errorbar(aes(ymin=REAC_TIME_CT -se, ymax=REAC_TIME_CT+se), colour="black", width=.1, position=pd, size = 1) +
    geom_line(position=pd, size = 1.1) +
    geom_point(position=pd, size=3, shape=21, fill="white") + # 21 is filled circle
    xlab("AGE GROUPS (years)") +
    ylab("Reaction Time (sec)") +
    scale_colour_hue(name = "Birth Experience",
                     breaks=c("C", "V"),
                     labels=c("C-section", "Vaginal"),
                     l=40) + 
    theme(legend.position = "bottom")+ 
    ggtitle("Reaction Time in Each Trial Condition for Birth Experience") + # Use darker colors, lightness=40
    expand_limits(y=c(0.2, 0.6)) +                        # Expand y range
    theme_bw()
   
```

# For the Full Data

## Check assumptions

```{r assumptions}
# Outliers - Accuracy
data1 %>%
  group_by(AGE_GROUPS, TRIAL_TYPE, BIRTH_EXP) %>%
  identify_outliers(ACCURACY)

# Normality  - Accuracy
data1 %>%
  group_by(AGE_GROUPS, TRIAL_TYPE, BIRTH_EXP) %>%
  shapiro_test(ACCURACY)

# Outliers - Reaction Time
data1 %>%
  group_by(AGE_GROUPS, TRIAL_TYPE, BIRTH_EXP) %>%
  identify_outliers(REAC_TIME_CT)

# Normality - Reaction Time
data1 %>%
  group_by(AGE_GROUPS, TRIAL_TYPE, BIRTH_EXP) %>%
  shapiro_test(REAC_TIME_CT)
```

Participant 205 - extreme outlier for Vaginal, cue, age group 3


## ANOVA - ACCURACY - Full data

```{r ANOVA 1}
# IV- Birth Experience and Age Groups, DV - Accuracy

model1 <- aov(ACCURACY~BIRTH_EXP+AGE_GROUPS+TRIAL_TYPE, data= data1)
summary (model1)

int_mod1 <- aov (ACCURACY~ BIRTH_EXP*AGE_GROUPS*TRIAL_TYPE, data= data1)
summary (int_mod1)

effectsize::eta_squared(int_mod1)

# options(contrasts = c("contr.sum", "contr.poly"))
# lm_output <- lm(ACCURACY ~ BIRTH_EXP*AGE_GROUPS*TRIAL_TYPE, data = data1)
# summary (lm_output)
# # apa.aov.table(lm_output)
# apa.2way.table(BIRTH_EXP, AGE_GROUPS, ACCURACY, data = data1)
# levels (data1$BIRTH_EXP)
# summary.lm(model1)
# summary.lm(int_mod1)


```

### Pairwise - Accuracy
```{r pairwise}
## Pairwise t-test to check for interaction effects
pairwise.t.test(d1$ACCURACY, d1$BIRTH_EXP, p.adj = "bonf")
pairwise.t.test(d2$ACCURACY, d2$BIRTH_EXP, p.adj = "bonf")
pairwise.t.test(d3$ACCURACY, d3$BIRTH_EXP, p.adj = "bonf")
```
1. There is a main effect of Trial type (cue and no cue) in accuracy 
2. There is an interaction effect between birth experience and age groups.


### Planned contrasts - AGE_GROUP>>BIRTH_EXPERIENCE - ACCURACY

```{r pc datasets, echo=FALSE}
data4 <- data1 %>%
  filter (AGE < 9) %>%
  select (ID, AGE, BIRTH_EXP, DIS,TRIAL_TYPE, REAC_TIME, ACCURACY, REAC_TIME_CT)
data5 <- data1 %>%
  filter (AGE<12 & AGE>8) %>%
  select (ID, AGE, BIRTH_EXP, DIS,TRIAL_TYPE, REAC_TIME, ACCURACY, REAC_TIME_CT)
data6 <- data1 %>%
  filter (AGE>11) %>%
  select (ID, AGE, BIRTH_EXP, DIS,TRIAL_TYPE, REAC_TIME, ACCURACY, REAC_TIME_CT)

data4_V <- data4 %>%
  filter (BIRTH_EXP == 'V')
data4_C <- data4 %>%
  filter (BIRTH_EXP == 'C')

data5_V <- data5 %>%
  filter (BIRTH_EXP == 'V')
data5_C <- data5 %>%
  filter (BIRTH_EXP == 'C')

data6_V <- data6 %>%
  filter (BIRTH_EXP == 'V')
data6_C <- data6 %>%
  filter (BIRTH_EXP == 'C')

```

```{r planned contrasts accuracy 1}

contr <- c(-1, 1)


## Age Group 1
mod1 <- aov(ACCURACY~BIRTH_EXP, data= data4)
GS_1 <- glht(mod1,
linfct = mcp(BIRTH_EXP = contr))
summary(GS_1)

## Age Group 2
mod2 <- aov(ACCURACY~BIRTH_EXP, data= data5)
GS_2<- glht(mod2,
linfct = mcp(BIRTH_EXP = contr))
summary(GS_2)

## Age Group 3
mod3 <- aov(ACCURACY~BIRTH_EXP, data= data6)
GS_3<- glht(mod3,
linfct = mcp(BIRTH_EXP = contr))
summary(GS_3)

```

### Planned contrasts - AGE_GROUP>>BIRTH_EXPERIENCE>>>TRIAL_TYPE - ACCURACY

```{r planned contrasts accuracy 2}

contrC_N <- c(1, -1)


## Age Group 1

mod4_V <- aov(ACCURACY~TRIAL_TYPE, data= data4_V)
GS_4V <- glht(mod4_V,
linfct = mcp(TRIAL_TYPE = contrC_N))
summary(GS_4V)

mod4_C <- aov(ACCURACY~TRIAL_TYPE, data= data4_C)
GS_4C <- glht(mod4_C,
linfct = mcp(TRIAL_TYPE = contrC_N))
summary(GS_4C)

## Age Group 2
mod5_V <- aov(ACCURACY~TRIAL_TYPE, data= data5_V)
GS_5V <- glht(mod5_V,
linfct = mcp(TRIAL_TYPE = contrC_N))
summary(GS_5V)

mod5_C <- aov(ACCURACY~TRIAL_TYPE, data= data5_C)
GS_5C <- glht(mod5_C,
linfct = mcp(TRIAL_TYPE = contrC_N))
summary(GS_5C)


## Age Group 3
mod6_V <- aov(ACCURACY~TRIAL_TYPE, data= data6_V)
GS_6V <- glht(mod6_V,
linfct = mcp(TRIAL_TYPE = contrC_N))
summary(GS_6V)

mod6_C <- aov(ACCURACY~TRIAL_TYPE, data= data6_C)
GS_6C <- glht(mod6_C,
linfct = mcp(TRIAL_TYPE = contrC_N))
summary(GS_6C)

```

```{r Diagnostics 1}
par(mfrow=c(2,2))
plot(int_mod1)
```

## ANOVA - REACTION TIME OF CORRECT TRIALS - Full Data

```{r ANOVA2}
# IV- Birth Experience and Age Groups, DV - Reaction Time

model2 <- aov(REAC_TIME_CT~ BIRTH_EXP+AGE_GROUPS+TRIAL_TYPE, data = data1)
summary(model2)

int_mod2 <- aov (REAC_TIME_CT~BIRTH_EXP*AGE_GROUPS*TRIAL_TYPE, data= data1)
summary (int_mod2)

options(contrasts = c("contr.sum", "contr.poly"))
lm_output2 <- lm(REAC_TIME ~ BIRTH_EXP*AGE_GROUPS*TRIAL_TYPE, data = data1)
apa.aov.table(lm_output2)

apa.2way.table(BIRTH_EXP, AGE_GROUPS, REAC_TIME, data = data1)

```

1. There is a main effect of Trial type (cue and no cue) on reaction time in correct trials




### Planned contrasts - Birth Experience differences in each Age group - REACTION TIME

```{r planned contrasts reaction time 1}

contr <- c(-1, 1)

## Age Group 1
mod1.1 <- aov(REAC_TIME_CT~BIRTH_EXP, data= data4)
GS_1.1 <- glht(mod1.1,
linfct = mcp(BIRTH_EXP = contr))
summary(GS_1.1)

## Age Group 2
mod2.1 <- aov(REAC_TIME_CT~BIRTH_EXP, data= data5)
GS_2.1 <- glht(mod2.1,
linfct = mcp(BIRTH_EXP = contr))
summary(GS_2.1)

## Age Group 3
mod3.1 <- aov(REAC_TIME_CT~BIRTH_EXP, data= data6)
GS_3.1 <- glht(mod3.1,
linfct = mcp(BIRTH_EXP= contr))
summary(GS_3.1)
```

### Planned contrasts - AGE_GROUP>>BIRTH_EXPERIENCE>>>TRIAL_TYPE - REACTION TIME

```{r planned contrasts reaction time 2}
contrC_N <- c(1, -1)


## Age Group 1

mod4_V.1 <- aov(REAC_TIME_CT~TRIAL_TYPE, data= data4_V)
GS_4V.1 <- glht(mod4_V.1,
linfct = mcp(TRIAL_TYPE = contrC_N))
summary(GS_4V.1)

mod4_C.1 <- aov(REAC_TIME_CT~TRIAL_TYPE, data= data4_C)
GS_4C.1 <- glht(mod4_C.1,
linfct = mcp(TRIAL_TYPE = contrC_N))
summary(GS_4C.1)

## Age Group 2
mod5_V.1 <- aov(REAC_TIME_CT~TRIAL_TYPE, data= data5_V)
GS_5V.1 <- glht(mod5_V.1,
linfct = mcp(TRIAL_TYPE = contrC_N))
summary(GS_5V.1)

mod5_C.1 <- aov(REAC_TIME_CT~TRIAL_TYPE, data= data5_C)
GS_5C.1 <- glht(mod5_C.1,
linfct = mcp(TRIAL_TYPE = contrC_N))
summary(GS_5C.1)


## Age Group 3
mod6_V.1 <- aov(REAC_TIME_CT~TRIAL_TYPE, data= data6_V)
GS_6V.1 <- glht(mod6_V.1,
linfct = mcp(TRIAL_TYPE = contrC_N))
summary(GS_6V.1)

mod6_C.1 <- aov(REAC_TIME_CT~TRIAL_TYPE, data= data6_C)
GS_6C.1 <- glht(mod6_C.1,
linfct = mcp(TRIAL_TYPE = contrC_N))
summary(GS_6C.1)

```


```{r Diagnostics 2}
par(mfrow=c(2,2))
plot(int_mod2)
```


# For each Trial Condition

## Cue Trials

### 1. TWO-WAY ANOVA - ACCURACY 

```{r ANOVA 3}
# IV- Birth Experience and Age Groups, DV - Accuracy

model3 <- aov(ACCURACY~BIRTH_EXP+AGE_GROUPS, data = data2)
summary (model3)

int_mod3 <- aov (ACCURACY~ BIRTH_EXP*AGE_GROUPS, data= data2)
summary (int_mod3)
TukeyHSD(int_mod3)

options(contrasts = c("contr.sum", "contr.poly"))
lm_output3 <- lm(ACCURACY ~ BIRTH_EXP*AGE_GROUPS, data = data2)
summary (lm_output3)
apa.aov.table(lm_output3)

```

```{r Diagnostics 3}
plot(int_mod3)
```

### 2. TWO-WAY ANOVA - REACTION TIME 

```{r ANOVA4}
# IV- Birth Experience and Age Groups, DV - Reaction Time

model4 <- aov(REAC_TIME_CT~ BIRTH_EXP+AGE_GROUPS, data = data2)
summary(model4)

int_mod4 <- aov (REAC_TIME_CT~BIRTH_EXP*AGE_GROUPS, data= data2)
summary (int_mod4)
TukeyHSD(int_mod4)

options(contrasts = c("contr.sum", "contr.poly"))
lm_output4 <- lm(REAC_TIME_CT ~ BIRTH_EXP*AGE_GROUPS, data = data2)
apa.aov.table(lm_output4)
```

```{r Diagnostics 4}
plot(int_mod4)
```








## No Cue Trials

### 1. TWO-WAY ANOVA - ACCURACY 

```{r ANOVA 5}
# IV- Birth Experience and Age Groups, DV - Accuracy

model5 <- aov(ACCURACY~BIRTH_EXP+AGE_GROUPS, data = data3)
summary (model5)

int_mod5 <- aov (ACCURACY~ BIRTH_EXP*AGE_GROUPS, data= data3)
summary (int_mod5)
TukeyHSD(int_mod5)

options(contrasts = c("contr.sum", "contr.poly"))
lm_output5 <- lm(ACCURACY ~ BIRTH_EXP*AGE_GROUPS, data = data3)
apa.aov.table(lm_output5)

```

```{r Diagnostics 5}
plot(int_mod5)
```

### 2. TWO-WAY ANOVA - REACTION TIME 

```{r ANOVA 6}
# IV- Birth Experience and Age Groups, DV - Reaction Time

model6 <- aov(REAC_TIME_CT~ BIRTH_EXP+AGE_GROUPS, data = data3)
summary(model6)

int_mod6 <- aov (REAC_TIME_CT~BIRTH_EXP*AGE_GROUPS, data= data3)
summary (int_mod6)
TukeyHSD(int_mod6)

options(contrasts = c("contr.sum", "contr.poly"))
lm_output6 <- lm(REAC_TIME_CT ~ BIRTH_EXP*AGE_GROUPS, data = data3)
apa.aov.table(lm_output6)
```

```{r Diagnostics 6}
plot(int_mod6)
```

# Age Group 1 - 6 to 8 years analysis
```{r creating groups for age group1}
data4_V$AGE_GRP <- factor(data4_V$AGE)
data4_C$AGE_GRP <- factor(data4_C$AGE)

data4_V6_cue <- filter(data4_V, AGE_GRP == 6, TRIAL_TYPE == "Cue")
data4_V6_nocue <- filter(data4_V, AGE_GRP == 6, TRIAL_TYPE == "NoCue")
sample_V6_cue <- data4_V6_cue [sample(nrow(data4_V6_cue ), 3), ]
sample_V6_cue$ID <- temp1
data4_V6_nocue <- subset(data4_V6_nocue, ID!= any(temp1))
filter (data4_V6_nocue, ID != sample_V6_cue$ID)



sample_V6_nocue <- data4_V6_nocue [sample(nrow(data4_V6_nocue ), 3), ]
temp1 <-  sample_V6_cue$ID


sample_V6_nocue <-  data4_V6_nocue[sample(nrow(data4_V6_nocue ), 3), ]
sample_V6

data4_C6_cue <- filter(data4_C, AGE_GRP == 6, TRIAL_TYPE == "Cue")
data4_C6_nocue <- filter(data4_C, AGE_GRP == 6, TRIAL_TYPE == "NoCue")
sample_C6_cue <- data4_C6_cue [sample(nrow(data4_C6_cue ), 3, replace = F), ]
sample_C6_nocue <- data4_C6_nocue [sample(nrow(data4_C6_nocue ), 3,replace = F), ]


data4_V7_cue <- filter(data4_V, AGE_GRP == 7, TRIAL_TYPE == "Cue")
data4_V7_nocue <- filter(data4_V, AGE_GRP == 7, TRIAL_TYPE == "NoCue")
sample_V7_cue <- data4_V7_cue [sample(nrow(data4_V7_cue ), 3, replace = F), ]
sample_V7_nocue <- data4_V7_nocue [sample(nrow(data4_V7_nocue ), 3,replace = F), ]

data4_C7_cue <- filter(data4_C, AGE_GRP == 7, TRIAL_TYPE == "Cue")
data4_C7_nocue <- filter(data4_C, AGE_GRP == 7, TRIAL_TYPE == "NoCue")
sample_C7_cue <- data4_C7_cue [sample(nrow(data4_C7_cue ), 3, replace = F), ]
sample_C7_nocue <- data4_C7_nocue [sample(nrow(data4_C7_nocue ), 3,replace = F), ]

data4_V8_cue <- filter(data4_V, AGE_GRP == 8, TRIAL_TYPE == "Cue")
data4_V8_nocue <- filter(data4_V, AGE_GRP == 8, TRIAL_TYPE == "NoCue")
sample_V8_cue <- data4_V8_cue [sample(nrow(data4_V8_cue ), 3, replace = F), ]
sample_V8_nocue <- data4_V8_nocue [sample(nrow(data4_V8_nocue ), 3,replace = F), ]

data4_C8_cue <- filter(data4_C, AGE_GRP == 8, TRIAL_TYPE == "Cue")
data4_C8_nocue <- filter(data4_C, AGE_GRP == 8, TRIAL_TYPE == "NoCue")
sample_C8_cue <- data4_C8_cue [sample(nrow(data4_C8_cue ), 3, replace = F), ]
sample_C8_nocue <- data4_C8_nocue [sample(nrow(data4_C8_nocue ), 3,replace = F), ]

sample <- rbind (sample_V6_cue, sample_V6_nocue, sample_C6_cue, sample_C6_nocue,sample_V7_cue, sample_V7_nocue, sample_C7_cue, sample_C7_nocue, sample_V8_cue,sample_V8_nocue, sample_C8_cue, sample_C8_nocue)



```

## Accuracy



### Graph

```{r Graph Age Group1_acc}
# Graph 1 for Retrieval Phase 1
g1_graph_acc <- summarySE(sample, measurevar="ACCURACY", groupvars=c("AGE_GRP","BIRTH_EXP","TRIAL_TYPE"))
head (g1_graph_acc)

pd <- position_dodge(0.1)
ggplot(g1_graph_acc, aes(x=AGE_GRP , y= ACCURACY, group=BIRTH_EXP, color=BIRTH_EXP)) + 
  facet_grid(TRIAL_TYPE~.)+
    geom_errorbar(aes(ymin=ACCURACY-se, ymax=ACCURACY+se), colour="black", width=.1, position=pd, size = 1) +
    geom_line(position=pd, size = 1.1) +
    geom_point(position=pd, size=3, shape=21, fill="white") + # 21 is filled circle
    xlab("AGE GROUPS (years)") +
    ylab("ACCURACY") +
    scale_colour_hue(name = "Birth Experience",
                     breaks=c("C", "V"),
                     labels=c("C-section", "Vaginal"),
                     l=40) + 
    theme(legend.position = "bottom")+ 
    ggtitle("Accuracy in Each Trial Condition for Birth Experience") + # Use darker colors, lightness=40
    expand_limits(y=c(0.2, 0.6)) +                        # Expand y range
    theme_bw()
   
```

### ANOVA 

```{r age1 accuracy}
model7 <- aov(ACCURACY~ AGE_GRP+BIRTH_EXP+TRIAL_TYPE, data = sample)
summary(model7)

int_mod7 <- aov (ACCURACY~AGE_GRP*BIRTH_EXP*TRIAL_TYPE, data= sample)
summary (int_mod7)
TukeyHSD(int_mod7)
```

## Reaction Time

### Graph

```{r Graph Age Group1_rt}
# Graph 1 for Retrieval Phase 1
g1_graph_rt <- summarySE(sample, measurevar="REAC_TIME_CT", groupvars=c("AGE_GRP","BIRTH_EXP","TRIAL_TYPE"))
head (g1_graph_rt)

pd <- position_dodge(0.1)
ggplot(g1_graph_rt, aes(x=AGE_GRP , y= REAC_TIME_CT , group=BIRTH_EXP, color=BIRTH_EXP)) + 
  facet_grid(TRIAL_TYPE~.)+
    geom_errorbar(aes(ymin=REAC_TIME_CT -se, ymax=REAC_TIME_CT+se), colour="black", width=.1, position=pd, size = 1) +
    geom_line(position=pd, size = 1.1) +
    geom_point(position=pd, size=3, shape=21, fill="white") + # 21 is filled circle
    xlab("AGE GROUPS (years)") +
    ylab("Reaction Time (sec)") +
    scale_colour_hue(name = "Birth Experience",
                     breaks=c("C", "V"),
                     labels=c("C-section", "Vaginal"),
                     l=40) + 
    theme(legend.position = "bottom")+ 
    ggtitle("Reaction Time in Each Trial Condition for Birth Experience") + # Use darker colors, lightness=40
    expand_limits(y=c(0.2, 0.6)) +                        # Expand y range
    theme_bw()
   
```

### ANOVA

```{r age1 reaction time}
model7.2 <- aov(REAC_TIME_CT~ AGE_GRP+BIRTH_EXP+TRIAL_TYPE, data = sample)
summary(model7.2)

int_mod7.2 <- aov (REAC_TIME_CT~AGE_GRP*BIRTH_EXP*TRIAL_TYPE, data= sample)
summary (int_mod7.2)
TukeyHSD(int_mod7.2)
```

