---
title: "OSC_Data_Analysis"
author: "Aarthi Ravi"
date: "18/06/2021"
output:
  pdf_document: default
  html_document: default
  word_document: default
---
```{r setup}
require("knitr")
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(tidy.opts=list(width.cutoff=50),tidy=TRUE)

library(data.table)
library(tidyverse)
library(magrittr)
library(car)
library(gridExtra)
library(psych)
library(ggplot2)
library(multcomp)
library(plotly)
library(apaTables)
library(dplyr)
```

# Import Datasets - Full data and Data of correct trials only
```{r data}
data <- read.csv ("OSC_cleaned.csv")
data_ct <- read.csv ("OSC_cleaned_ct.csv")
```

# Descriptives/ Preliminary Analyses
```{r descriptives data}
data1 <- select (data, ID, AGE, BIRTH_EXP, DIS, REAC_TIME, ACCURACY)
head (data1)
summary (data1)
describe (data1)
```

# Table : Number of Participants in each Group
```{r descriptives table, echo =FALSE}
d1 <- filter (data1, AGE < 9 )
d2 <- filter (data1, (AGE<12 & AGE>8))
d3 <- filter (data1, AGE>11)
d4 <- filter (data1, BIRTH_EXP == "V")
d5 <- filter (data1, BIRTH_EXP == "C")
d6 <- filter (data1, DIS == "Y")


number_group <- c(nrow(d1),nrow(d2),nrow(d3),nrow(d4),nrow(d5),nrow(d6))
part_demographics <- data.frame(cbind(nrow(d1),nrow(d2),nrow(d3),nrow(d4),nrow(d5),nrow(d6)))

names (part_demographics) <- c("Age_Group1 (6 to 8 yrs)", "Age_Group2 (9 to 11 yrs)", "Age_Group3 (12< yrs)", "Vaginally_born", "C-sec_born", "Gen_dis")


kable (part_demographics, align = "cccccc")
```




# Descriptives/ Preliminary Analyses Correct Trials
```{r descriptives data correct trials}
data2 <- select (data_ct, ID, AGE, BIRTH_EXP, DIS, REAC_TIME)
head (data2)
summary (data2)
describe (data2)
```


```{r Factors , echo=FALSE}
# Creating factors
data1$AGE_GROUPS <- factor(data1$AGE)
data1$AGE_GROUPS <- data1$AGE
data1$AGE_GROUPS[which(data1$AGE < 9)]<- "1"
data1$AGE_GROUPS[which(data1$AGE<12 & data1$AGE>8)]<- "2"
data1$AGE_GROUPS[which(data1$AGE > 11)]<- "3"

data1$AGE_GROUPS <- as.factor (data1$AGE_GROUPS)
data1$BIRTH_EXP <- as.factor (data1$BIRTH_EXP)



# Creating factors correct trials
data2$AGE_GROUPS <- factor(data2$AGE)
data2$AGE_GROUPS <- data2$AGE
data2$AGE_GROUPS[which(data2$AGE < 9)]<- "1"
data2$AGE_GROUPS[which(data2$AGE<12 & data2$AGE>8)]<- "2"
data2$AGE_GROUPS[which(data2$AGE > 11)]<- "3"

data2$AGE_GROUPS <- as.factor (data2$AGE_GROUPS)
data2$BIRTH_EXP <- as.factor (data2$BIRTH_EXP)
```


# Table : Number of Participants in Each Age Group and their Birth Experience
```{r descriptives table 2}
table(data1$BIRTH_EXP,data1$AGE_GROUPS)
```

# Table : Number of Participants with Disability and their Birth Experience 
```{r descriptives table 3}
table(data1$BIRTH_EXP,data1$DIS)
```

# Data Distribution Plots

```{r plots}
# Boxplot for Accuracy in Trials and Birth Experience
qplot(AGE_GROUPS, ACCURACY, data=data1, fill = BIRTH_EXP, geom = 'boxplot', main = "Mixed ANOVA", xlab = "AGE GROUPS",ylab = "ACCURACY")

# Boxplot for Reaction Time in Correct Trials and Birth Experience
qplot(AGE_GROUPS, REAC_TIME, data=data2, fill = BIRTH_EXP, geom = 'boxplot', main = "Mixed ANOVA",xlab = "AGE GROUPS", ylab = "REACTION TIME")

```

# Bar Graph Accuracy vs Age-Groups
```{r barplot}

ggplot(data1, aes(BIRTH_EXP, ACCURACY, fill = AGE_GROUPS)) + 
  geom_bar(stat="identity", position = "dodge", width=0.3) + 
  scale_fill_brewer(palette = "Set1", labs(y="Age Groups"))

ggplot(data1, aes(AGE_GROUPS, ACCURACY, fill = BIRTH_EXP)) + 
  geom_bar(stat="identity", position = "dodge", width=0.3) + 
  scale_fill_brewer(palette = "Set1", labs(y="Birth Experience"))
```

# Bar Graph Reaction Time vs Age-Groups
```{r barplot2}
ggplot(data1, aes(BIRTH_EXP, REAC_TIME, fill = AGE_GROUPS)) + 
  geom_bar(stat="identity", position = "dodge",  width=0.3) + 
  scale_fill_manual(values = c("violet","pink", "orange"), labs(y="Age Groups"))

ggplot(data1, aes(AGE_GROUPS, REAC_TIME, fill = BIRTH_EXP)) + 
  geom_bar(stat="identity", position = "dodge", width=0.3) + 
 scale_fill_manual(values = c("violet", "pink" ), labs(y="Birth Experience"))
```


```{r scatterplot}
# Scatterplot

aggregated <- ggplot(data2, aes(AGE, REAC_TIME, colour=BIRTH_EXP)) + geom_point()+ labs(x = "Age", y = "Reaction Time") 

facetted <-data2 %>%
ggplot(aes(x=AGE, y = REAC_TIME, color = BIRTH_EXP)) +
geom_point() +
facet_grid(cols = vars(AGE_GROUPS), rows = vars(BIRTH_EXP)) +
labs(x = "Age Groups", y = "Reaction Time") +
theme_bw() +
theme(legend.position="none")

grid.arrange(facetted, aggregated, ncol = 2)
```




#TWO-WAY ANOVA - ACCURACY
```{r ANOVA}
# IV- Birth Experience and Age Groups, DV - Reaction Time

model1 <- aov(ACCURACY~BIRTH_EXP+AGE_GROUPS, data = data1)
summary (model1)

int_mod1 <- aov (ACCURACY~BIRTH_EXP*AGE_GROUPS, data= data1)
summary (int_mod1)
TukeyHSD(int_mod1)

options(contrasts = c("contr.sum", "contr.poly"))
lm_output <- lm(ACCURACY ~ BIRTH_EXP*AGE_GROUPS, data = data1)
apa.aov.table(lm_output)

apa.2way.table(BIRTH_EXP, AGE_GROUPS, ACCURACY, data = data1)
```
```{r Diagnostics 1}
plot(int_mod1)
```


```{r Accuracy interaction plot}

with (data1, {
  interaction.plot(AGE_GROUPS, BIRTH_EXP, ACCURACY, fun = mean,
                type = c("l", "p", "b", "o", "c"), legend = TRUE,
                trace.label = "Birth Experience",
                fixed = TRUE,
                col = c ("red", "blue"),
                lty = 1,
                xlab = "Age Groups",
                ylab = "Accuracy")
                
               
})
                

```





#TWO-WAY ANOVA - REACTION TIME
```{r ANOVA2}
# IV- Birth Experience and Age Groups, DV - Reaction Time

model2 <- aov(REAC_TIME~ BIRTH_EXP+AGE_GROUPS, data = data2)
summary(model2)

int_mod2 <- aov (REAC_TIME~BIRTH_EXP*AGE_GROUPS, data= data2)
summary (int_mod2)

options(contrasts = c("contr.sum", "contr.poly"))
lm_output2 <- lm(REAC_TIME ~ BIRTH_EXP*AGE_GROUPS, data = data2)
apa.aov.table(lm_output2)

apa.2way.table(BIRTH_EXP, AGE_GROUPS, REACT_TIME, data = data1)
```


```{r Diagnostics 2}
plot(int_mod2)
```


